### 2019-09-13 theme.tex
adds some images

There are many challenges facing the world today. Some of these have been designated existential threats to humanity. As students, these obstacles may appear insurmountable. The ANS Student Conference is a marvelous opportunity to inspire optimism for the future as researchers, professionals, and others students, gather to showcase critical advances in technology. Whether the problem is solving the world's energy needs, developing technology to take us to the stars, or curing cancer, nuclear, plasma, and radiological engineering will be at the center of those endeavors. Our goal is to inspire and motivate students in these fields to tackle these grand challenge problems. Students will hear from visionary speakers and leaders of the nuclear science community. They will leave with renewed hope for the future and the knowledge that their efforts are saving the world, one atom at a time.\\
The University of Illinois at Urbana-Champaign would honored to host the ANS Student Conference in 2021 and to share the innovative and galvanizing environment of our great campus.

>>>>

There are many challenges facing the world today. Some of these have been designated existential threats to humanity. As students, these obstacles may appear insurmountable. The ANS Student Conference is a marvelous opportunity to inspire optimism for the future as researchers, professionals, and students, gather to showcase critical advances in technology. Nuclear, plasma, and radiological engineering will be central to endeavors like solving the world's energy needs, developing technology that will take us to the stars, treating cancer, and many others.  Our goal is to inspire and motivate students in these fields to tackle grand challenge problems. Students will hear from visionary speakers and leaders of the nuclear science community. They will leave with renewed hope for the future and the knowledge that their efforts are saving the world, one atom at a time.\\
The University of Illinois at Urbana-Champaign would honored to host the ANS Student Conference in 2021 and to share the innovative and galvanizing environment of our great campus.
